Adopting agile in the large: motivations, success factors and challenges

### 2014-05-05 journal/article.tex
Work in progress

@@

>>>>

WORKING IN SILOS --> Certain expertise is required in many places

* Teams were reorganized without notice --> Planning was hampered when people did not konw who would stay on a team
* Frequent changes --> People managers had to agree to minimize team changes
[P11]
When we launched multiple Scrum teams, we tried to keep existing teams together
and form new teams based on skills.  As we gained experience, we realized that
there were skills shortages in certain types of expertise that wasn’t possible
to develop in a sprint or two. There was pressure to move engineers with certain
skills to the teams that needed them for work on upcoming sprints or to address
critical customer requirements.  When moves occurred without much notice, teams
couldn’t plan effectively if they didn’t know who would stay on a team.  After
several months of frequent changes, product owners and people managers agreed to
minimize team changes, and even talked of instituting a “trading deadline.”

@@

* Some success factors and challenges relate

* Success factors and challenges may be complements, and may be presented as
  complements

* What is special in large scale?

* What is similar in organizations of all scales?
